On The Statistical Properties of Cospectra

### 2017-12-04 paper/referee_response.md

> Re. (i) Even for large Signal-to-noise (S/N) the co-spectrum is entirely insensitive to some oscillations with wrong phase. To my knowledge, no else known method suffers
> from such a weakness. Though remedies exist, the distributions discussed in the paper do not apply to them.

and

> 2. Re. (ii) and (iii) Fig. 3 reveals that the simulations were set up so, that the inserted oscillation remains in phase with the reference signal component, resulting with a large positive peak at the corresponding frequency. In the real word, the phases would be randomly distributed and both positive, negative and near null values would be observed.

> 1. Re. (i) The co-spectrum is real part of product of transforms of the reference and investigated signal. At any given frequency if actual oscillation differs in phase by 90/270 degrees from the phase of reference/noise signal component, the result co-spectrum value is null. As consequence, there is a range of phases for which even an oscillation with strong S/N remains undetectable. A remedy, namely to investigate several phase offsets, wold spoil the claimed for distributions and introduce mutual correlations difficult to analyze. This issue is nowhere discussed in the text.
